---
title: "FAQ"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
options(scipen = 999)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 12
)
```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 800)
#opts_chunk$set(tidy = F)
#blogify
```



***

### FAQ
This FAQ ...
***

## Accounts

#### I can't see my organizer's info
This could be due to your having multiple accounts, one that you created with your phone number, and another with your email address, each with different permissions. 

### Regions

#### Why can't I see my regions?
fks;jfkd; kl;ds fks;f jk;f sk;fs;kf

### Call To Action (CTA)

#### How can I change my question in the CTA?
To change a CTA, you must delete the CTA and create a new one

#### I can't ....
Filtering will be added soon to the app


<br/><br/><br/>






